---
title: "Instructions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Instructions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
library(dplyr)
library(stringr)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(c4aRs)
```


This package is meant to provide support to R users at C4. It contains resources for working with Seizure data, some dplyr tools, the C4 color palettes, and some miscellaneous tools. Below are a few examples. This package is meant as a supplement to existing tidyverse functions.


# Seizure Data Resources

```{r}

seiz_dat <- 
  tribble(
  ~Year, ~Type, ~Seizure, ~Origin, ~Transit, ~Destination,
    2010, 'Wildlife', 'China', 'Mexico', 'Belgium', 'China',
    2010, 'Drugs', 'USA', 'Panama', 'USA', 'China',
    2016, 'Firearms', 'China', 'South Africa', 'Qatar', 'China',
    2019, 'Wildlife', 'China', 'Mexico', 'UAE', 'China',
    )

countryCols <- 
  c('Seizure', 
      'Origin', 
      'Transit', 
      'Destination')
  

```

## Trafficking Instance Counts 

To get TI count for all countries in the dataset, use `traffickingInstanceCount` without an argument for `by_col`.

```{r}
seiz_dat %>% 
  traffickingInstanceCount(cols = countryCols)
```

Use the `by_col` to get TI count by that specific column. 


```{r}
seiz_dat %>% 
  traffickingInstanceCount(cols = countryCols, by_col = "Type")
```



```{r}
seiz_dat %>% 
  traffickingInstanceCount(cols = countryCols, by_col = "Year")
```


## Trafficking Instances 

To get all rows that contain trafficking instances for a given country (or multiple), use `selectByMultCols`. This selects all rows that have an entry that appears in the `values` argument in one of the `cols`.

```{r}
# get all Mexico TIs
seiz_dat %>% 
  selectByMultCols(cols = countryCols, values = "Mexico")
```

```{r}
# get all North American TIs
north_america <- c("USA", "Mexico", "Canada")
seiz_dat %>% 
  selectByMultCols(cols = countryCols, values = north_america)
```


## Mapping/Plotting Resources

`leafletLabel` and `plotlyLabel` provide a way of easily adding tooltip labels to maps and graphs. Each adds a label column that will plug into `leaflet` or `plotly`. `textNames` and `colNames` are required, and there are options to add a title and change font sizes. 


```{r, eval = F}

locs <- 
  tribble(
  ~Loc, ~Long, ~Lat, ~Type, ~People,
    'A', 2.783629, 50.279807, 'Mine', 67,
    'B', 2.782419, 50.281229, 'Grocery Store', 323,
    'C', 2.780950, 50.287279, 'Train Station', 623,
    'D', 2.777744, 50.291332, 'Place', 1505
    )

```


```{r, eval = F}
library(leaflet)

locs %>% 
  leafletLabel(textNames = c("Place Type", "Number of People"), 
               colNames = c("Type", "People"), 
               titleCol = "Loc",
               titleSize = 2.8) %>% 
  leaflet() %>% 
  addTiles() %>% 
  addMarkers(
    lng = ~Long,
    lat = ~Lat,
    label = ~label %>% lapply(htmltools::HTML)
  )
  
    
```














